### 2023-06-16 resilience.tex
up
section 3

\begin{definition}
We say that $\mathscr{S}=(S, \rightarrow, \leq)$ is $X$-resilient (resp. $(s_0,X)$-resilient) if $S  \xrightarrow{*} X$ (resp. $\post^*(s_0) \xrightarrow{*} X$) is satisfied.  
\end{definition}

@@

>>>>

\begin{definition}
We say that $\mathscr{S}=(S, \rightarrow, \leq)$ is $X$-resilient if $S  \xrightarrow{*} X$ is satisfied.  
\end{definition}

@@

It is also possible to define $(s_0,X)$-resilient systems as satisfying $\post^*(s_0) \xrightarrow{*} X$.
